Model Comparison

### 2020-02-11 stats/model_comparison.Rmd
model comparison example for MH to check

```{r}
library(tidyverse)
#library(rwebppl)
#library(brms)
#library(coda)
#library(ggthemes)
library(readxl)
#library(ggpubr)
library(matrixStats)
library(data.table)
#library(bigmemory)

@@

data_comb <- data_comb_pre%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa), 
         source = "Data")
```

@@

# Pragmatic vs Global

```{r}
prag_global <- bind_rows(

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_prag.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "prag",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_global.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "global",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_global = prag - global) %>%
  na.omit(prag_vs_global) %>%
  summarise(prag_vs_global = logSumExp(prag_vs_global))
```

# Pragmatic vs Flat

```{r}

comp <- bind_rows(

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_prag.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "prag",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_flat.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "flat",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like)
)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_flat = prag - flat)

@@

# Pragmatic vs prior

```{r}

comp <- bind_rows(

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_prag.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "prag",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

  data_comb %>%
    select(-age)%>%
    mutate(age = age_month,
           item = as.character(item))%>%
    left_join(readRDS("../saves/model_pred_prior.rds"))%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
           log_like = log(like),
           model = "prior",
           id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_prior = prag - prior)

>>>>

```{r}
library(tidyverse)
library(readxl)
library(matrixStats)
library(data.table)

@@

data_comb <- data_comb_pre%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa), 
         source = "Data")

d_model_comp <- data_comb%>%
  select(-age)%>%
  mutate(age = round(age_month,2),
         item = as.character(item))%>%
  select(alignment, item, age, correct)

@@

## Dummy example for MH

```{r}
# Model prediction files are very large - can't put them on github as is 
# files below contain the two iterations for each model (1286 & 7185)

# load model predicitons
test_prag <- readRDS("../saves/test_prag.rds")
test_global <- readRDS("../saves/test_global.rds")
test_flat <- readRDS("../saves/test_flat.rds")

# join predictions with the data

bind_rows(

  test_prag %>%
    right_join(d_model_comp)%>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, correct),

  test_global %>%
    right_join(d_model_comp)%>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, correct),

   test_flat %>%
    right_join(d_model_comp)%>%
    mutate(id = 1:length(pred))%>%
    select(id, model,chain,iteration, age, alignment,item,pred, correct)
)%>%
  mutate(log_like = log(ifelse(correct == 1, pred, 1 - pred)))%>% # calculate log likelihood
  select(-pred, - correct)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
         prag_vs_flat= pragmatic - flat,
         global_vs_flat = global - flat) %>%
  summarise(prag_vs_global = sum(prag_vs_global), # sum up likelihood difference to get log Bayes factor
            prag_vs_flat = sum(prag_vs_flat),
            global_vs_flat = sum(global_vs_flat))%>%
  gather(model, logBF)

@@
